Machine learning high multiplicity matrix elements for electron-positron and hadron-hadron colliders

### 2023-03-13 intro.tex
improve ghost description

    To remove unphysical degrees of freedom from the
    theory we need to fix the gauge
    and add a ghost Lagrangian. The gauge-fixing term
    in the $R_{\xi}$ gauge is written as
    \begin{equation}\label{eqn:L_GF}
        \mathcal{L}_{\mathrm{GF}} = -\dfrac{1}{2\xi}(\partial^{\mu}A_{\mu}^{a})^{2} \, ,
    \end{equation}
    where $\xi = 1$ corresponds to the Feynman-'t Hooft gauge.
    Ghosts and antighosts are anti-commuting fields
    introduced for each gauge field as a way to conveniently compute
    determinants occurring in the gauge fixing procedure.
    The ghost Lagrangian is most commonly written
    in the Faddeev-Popov procedure as
    \begin{equation}\label{eqn:L_ghost}
        \mathcal{L}_{\mathrm{ghost}} = (\partial_{\mu}\bar{c}^{a})(\delta^{ac}\partial_{\mu} + g_{s}f^{abc}A^{b}_{\mu})c^{c} \, ,
    \end{equation}
    where $c^{a}$ ($\bar{c}^{a}$) are Faddeev-Popov ghosts (antighosts).
    The ghosts are unphysical particles and so cannot appear as
    external states. However, they must be included in internal lines for
    a gauge invariant theory as the ghost loops cancel the unphysical
    degrees of freedom in gluon loops.

>>>>

    To remove unphysical degrees of freedom from the
    theory we need to fix the gauge
    and add a ghost Lagrangian. The gauge-fixing term
    in the $R_{\xi}$ gauge is written as
    \begin{equation}\label{eqn:L_GF}
        \mathcal{L}_{\mathrm{GF}} = -\dfrac{1}{2\xi}(\partial^{\mu}A_{\mu}^{a})^{2} \, ,
    \end{equation}
    where $\xi = 1$ corresponds to the Feynman-'t Hooft gauge.
    Ghosts and antighosts are anti-commuting fields
    introduced for each gauge field as a way to conveniently compute
    determinants occurring in the gauge fixing procedure.
    The ghost Lagrangian is most commonly written
    in the Faddeev-Popov procedure as
    \begin{equation}\label{eqn:L_ghost}
        \mathcal{L}_{\mathrm{ghost}} = (\partial_{\mu}\bar{c}^{a})(\delta^{ac}\partial_{\mu} + g_{s}f^{abc}A^{b}_{\mu})c^{c} \, ,
    \end{equation}
    where $c^{a}$ ($\bar{c}^{a}$) are Faddeev-Popov ghosts (antighosts).
    Ghosts are particles that subtract the longitudinal
    degree of freedom from gluons, and as such it is usual to
    use them to cancel the longitudinal degree of freedom of gluon propagators.
    It should be noted that ghosts could in principle be included as external states as well
    for the same purpose, however, it is more conventional to use the usual physical polarisation sum
    instead.
